---
title: Sample post - Using SQL in R Markdown
summary: This post shows you how to use SQL in an R Markdown document
author: Danny Morris
date: '2021-04-23'
output:
  blogdown::html_page:
    highlight: tango
    toc: true
slug: []
Description: ''
Tags: [SQL, SQLite]
Categories: [SQL, SQLite]
DisableComments: no
editor_options: 
  chunk_output_type: console
---

## Overview

This sample post teaches you my preferred approach for authoring new posts that need to execute SQL code. The post includes a table of contents and code highlighting. The post content covers inserting and executing pure SQL code chunks and using R to execute SQL queries.

View the [source code](https://github.com/dannymorris/r4sites-anatole-custom/blob/master/content/english/post/2021-04-30-sample-post-using-sql-in-r-markdown/index.en.Rmd) on GitHub.

## Document metadata

As seen in the [source code](https://github.com/dannymorris/r4sites-anatole-custom/blob/master/content/english/post/2021-04-30-sample-post-using-sql-in-r-markdown/index.en.Rmd#L1-L17), the metadata is the information between the `---` markers at the top of the source code. Here is where you specify information such as the document author, date, summary, table of contents, code highlighting scheme, tags, and categories.

The metadata for this document contains the following information in the structure shown:

```
title: Sample post - Using SQL in R Markdown
summary: This post shows you how to use SQL in an R Markdown document
author: Danny Morris
date: '2021-04-30'
output:
  blogdown::html_page:
    highlight: tango
    toc: true
slug: []
Description: ''
Tags: [SQL, SQLite]
Categories: [SQL, SQLite]
DisableComments: no
editor_options: 
  chunk_output_type: console
```

## Load R packages

I prefer to load all R packages needed for the current document in a single code chunk near the top of the document.

```{r}
library(DBI)
library(RSQLite)
```

## Create and connect to a SQLite database

If you don't have access to an exisitng SQL database, use [SQLite](https://www.sqlite.org/index.html). SQLite is a local, serverless database application. SQLite is perfect for building small apps and practicing SQL.

```{r}
# create a SQLite db
db <- dbConnect(RSQLite::SQLite(), dbname = "mydb.sqlite")

# write the iris dataset to a table named IRIS
dbWriteTable(conn = db, name = "IRIS", value = iris, overwrite = T)
```

## Executing pure SQL code chunks

To insert and execute pure SQL directly inside an R Markdown document, create a `sql` code chunk. ([</> Code](https://github.com/dannymorris/r4sites-anatole-custom/blob/master/content/english/post/2021-04-30-sample-post-using-sql-in-r-markdown/index.en.Rmd)). Make sure you have an active database connection, as shown in the previous code chunk.

```{sql, connection=db}
SELECT Species, COUNT(1) as CNT 
FROM IRIS
GROUP BY Species
```

## Using R to execute SQL

To use R as a SQL client, use the `dbGetQuery()` function from the `DBI` R package to execute a SQL query. An active database connection is required. Note the following chunk is an `r` code chunk and not `sql`. [</> Code](https://github.com/dannymorris/r4sites-anatole-custom/blob/master/content/english/post/2021-04-30-sample-post-using-sql-in-r-markdown/index.en.Rmd#)

```{r}
DBI::dbGetQuery(
  conn = db,
  statement = "
  SELECT Species, COUNT(1) as CNT 
  FROM IRIS
  GROUP BY Species
  "
)
```



