---
title: Sample post - Using Python in R Markdown
summary: This post shows you how to use Python in an R Markdown document
author: Danny Morris
date: '2021-04-30'
output:
  blogdown::html_page:
    highlight: tango
    toc: true
slug: []
categories:
  - Python
  - R Markdown
  - Data Science
  - Conda
  - Machine Learning
tags:
  - Python
  - R Markdown
  - Data Science
  - Conda 
  - Machine Learning
Description: ''
Tags: []
Categories: []
DisableComments: no
---

## Overview

This post shows you how to insert Python code in a R Markdown document via the [reticulate](https://rstudio.github.io/reticulate/) R package.

```{r, include=F}
knitr::opts_chunk$set(message = F, warning = F, echo = T)
```

## Specify conda environment

This is optional but highly recommended. Using either Anaconda or Miniconda, create a conda environment with the libraries needed to run your analysis in Python. Using R, specify this conda enviornment with the `use_condaenv()` function from the `reticulate` package.

```{r}
# this is an R chunk
# all other chunks are Python
reticulate::use_condaenv("r-reticulate", required=T)
```

## Libraries

```{python}
import numpy as np
import matplotlib.pyplot as plt
from sklearn.ensemble import IsolationForest
```

## Fit isolation forest

```{python}
rng = np.random.RandomState(42)

# Generate train data
X = 0.3 * rng.randn(100, 2)
X_train = np.r_[X + 2, X - 2]
# Generate some regular novel observations
X = 0.3 * rng.randn(20, 2)
X_test = np.r_[X + 2, X - 2]
# Generate some abnormal novel observations
X_outliers = rng.uniform(low=-4, high=4, size=(20, 2))

# fit the model
clf = IsolationForest(max_samples=100, random_state=rng)
clf.fit(X_train)
```

## Predict outliers

```{python}
y_pred_train = clf.predict(X_train)
y_pred_test = clf.predict(X_test)
y_pred_outliers = clf.predict(X_outliers)
```

## Plot outliers

```{python}
# plot the line, the samples, and the nearest vectors to the plane
xx, yy = np.meshgrid(np.linspace(-5, 5, 50), np.linspace(-5, 5, 50))
Z = clf.decision_function(np.c_[xx.ravel(), yy.ravel()])
Z = Z.reshape(xx.shape)

plt.title("IsolationForest")
plt.contourf(xx, yy, Z, cmap=plt.cm.Blues_r)

b1 = plt.scatter(X_train[:, 0], X_train[:, 1], c='white',
                 s=20, edgecolor='k')
b2 = plt.scatter(X_test[:, 0], X_test[:, 1], c='green',
                 s=20, edgecolor='k')
c = plt.scatter(X_outliers[:, 0], X_outliers[:, 1], c='red',
                s=20, edgecolor='k')
plt.axis('tight')
plt.xlim((-5, 5))
plt.ylim((-5, 5))
plt.legend([b1, b2, c],
           ["training observations",
            "new regular observations", "new abnormal observations"],
           loc="upper left")
plt.show()
```

